Variation in distance between consecutive animal locations

### 2021-04-01 distributions_paper/rudolph_distributions.Rmd
eval r chunks for results

---
title: "Variation in distance between consecutive animal locations"
abstract: |
  This should be the abstract
output:
  html_document:
    df_print: paged
  word_document:
    reference_docx: docx_ref.docx
bibliography: aracari_refs.bib
csl: ecology-letters.csl
---

@@

```{r setup, include=FALSE}
# knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(message = FALSE, warning = FALSE, 
                      eval=FALSE,
                      echo = FALSE)

@@

```{r}
focus <- "dist15"

@@

```{r}
df %>% 
  ggplot(., aes(x = abs.angle)) +
  geom_histogram() +
  facet_wrap(~Bird_ID)
```

```{r}
df %>%
  drop_na(rel.angle) %>%
  mutate(d.angle = ifelse(rel.angle > 0, rel.angle * 180/pi,
                          rel.angle * 180/pi + 360)) %>%
  ggplot(., aes(x = d.angle)) +
  #facet_wrap(~id) +
  geom_histogram(color = "grey", fill = "grey") +
  coord_polar(theta = "x", start = -pi/2, direction = -1) +
  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "none")
```

@@

\newpage
# Questions  
* What is the distribution of distances between consecutive recorded locations? 
* Are there differences between individuals or can we use the same distribution to describe these distances between two locations?

The reasoning behind this, is that distances between locations can be used later on to describe variation in step length when simulating animal movement under simple models such as random walk.

@@

# Fit distribution  
Useful resource to use the package [fitdistrplus](https://cran.r-project.org/web/packages/fitdistrplus/vignettes/FAQ.html)
Also check [this](https://stackoverflow.com/questions/37152482/power-law-fitted-by-fitdistr-function-in-package-fitdistrplus). Should I do the opimization by hand?

@@

So, for each individual, which is the best fitting distribution, based on AIC or BIC? This is the distribution with the lowest AIC or BIC score for each individual. These are basically the distributions that will be used for the mixed distribution model later on.

```{r}
nice_prms %>% 
  filter(., str_detect(data, "B")) %>% 
  dplyr::select(dist, data, deltaAIC,
                #deltaAICc,
                deltaBIC) %>% 
  distinct() %>% 
  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
  filter(value == 0) %>%  
  pivot_wider(., names_from = ic, values_from = dist) %>% 
  mutate(agree = ifelse(deltaAIC == deltaBIC, paste(deltaBIC), paste(deltaBIC, "(BIC),", deltaAIC, "(AIC)"))) %>% 
  dplyr::select(., data, agree) %>% 
  rename(Individual = data,
            `Best model` = agree)
# 
# 
# nice_prms %>% 
#   filter(., data != "pop") %>% 
#   dplyr::select(dist, data, deltaAIC,
#                 #deltaAICc,
#                 deltaBIC) %>% 
#   distinct() %>% 
#   pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
#   filter(value > 0 & value <= 2) %>%  
#   pivot_wider(., names_from = ic, values_from = dist) %>% 
#   mutate(agree = ifelse(deltaAIC == deltaBIC, paste(deltaBIC), paste(deltaBIC, "(BIC),", deltaAIC, "(AIC)"))) %>% 
#   dplyr::select(., data, agree) %>% 
#   rename(Individual = data,
#             `Best model` = agree)

@@

gt_tbl %>% 
  tab_header(
    title = md("**Model comparisons across levels**")
  ) %>% 
  tab_stubhead(label = "Model") %>% 
  tab_row_group(
    group = "Multidist",
    rows = 9
  ) %>% 
  tab_row_group(
    group = "Individual",
    rows = 1:4
  ) %>% 
  tab_row_group(
    group = "Population", 
    rows = 5:8
  ) %>% 
  tab_spanner(
    label = md("**BIC**"),
    columns = vars(BIC, delta_BIC_within, delta_BIC_across)
  ) %>% 
  tab_spanner(
    label = md("**AIC**"),
    columns = vars(AIC, delta_AIC_within, delta_AIC_across)
  ) %>% 
  cols_label(
    delta_BIC_within = html("&Delta; BIC<sub>within</sub>"),
    delta_BIC_across = html("&Delta; BIC<sub>across</sub>"),
    delta_AIC_within = html("&Delta; AIC<sub>within</sub>"),
    delta_AIC_across = html("&Delta; AIC<sub>across</sub>")
  )

@@

```
# References

>>>>

---
title: "Variation in distance between consecutive animal locations"
abstract: |
  This should be the abstract
output:
  word_document:
    reference_docx: docx_ref.docx
  html_document:
    df_print: paged
bibliography: aracari_refs.bib
csl: ecology-letters.csl
---

@@

```{r setup, include=FALSE}
# knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(message = FALSE, warning = FALSE, 
                      #eval=FALSE,
                      echo = FALSE)

@@

```{r eval=FALSE}
focus <- "dist15"

@@

```{r eval=FALSE}
df %>% 
  ggplot(., aes(x = abs.angle)) +
  geom_histogram() +
  facet_wrap(~Bird_ID)
```

```{r eval=FALSE}
df %>%
  drop_na(rel.angle) %>%
  mutate(d.angle = ifelse(rel.angle > 0, rel.angle * 180/pi,
                          rel.angle * 180/pi + 360)) %>%
  ggplot(., aes(x = d.angle)) +
  #facet_wrap(~id) +
  geom_histogram(color = "grey", fill = "grey") +
  coord_polar(theta = "x", start = -pi/2, direction = -1) +
  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "none")
```

@@

\newpage

@@

# Fit distribution

@@

```{r}
nice_prms %>% 
  filter(., str_detect(data, "B")) %>% 
  dplyr::select(dist, data, deltaAIC,
                #deltaAICc,
                deltaBIC) %>% 
  distinct() %>% 
  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
  filter(value == 0) %>%  
  pivot_wider(., names_from = ic, values_from = dist) %>% 
  mutate(agree = ifelse(deltaAIC == deltaBIC, paste(deltaBIC), paste(deltaBIC, "(BIC),", deltaAIC, "(AIC)"))) %>% 
  dplyr::select(., data, agree) %>% 
  rename(Individual = data,
            `Best model` = agree) -> best_model

knitr::kable(best_model)
# 
# 
# nice_prms %>% 
#   filter(., data != "pop") %>% 
#   dplyr::select(dist, data, deltaAIC,
#                 #deltaAICc,
#                 deltaBIC) %>% 
#   distinct() %>% 
#   pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
#   filter(value > 0 & value <= 2) %>%  
#   pivot_wider(., names_from = ic, values_from = dist) %>% 
#   mutate(agree = ifelse(deltaAIC == deltaBIC, paste(deltaBIC), paste(deltaBIC, "(BIC),", deltaAIC, "(AIC)"))) %>% 
#   dplyr::select(., data, agree) %>% 
#   rename(Individual = data,
#             `Best model` = agree)

@@

gt_tbl %>% 
  tab_header(
    title = md("**Model comparisons across levels**")
  ) %>% 
  tab_stubhead(label = "Model") %>% 
  tab_row_group(
    group = "Multidist",
    rows = 9
  ) %>% 
  tab_row_group(
    group = "Individual",
    rows = 1:4
  ) %>% 
  tab_row_group(
    group = "Population", 
    rows = 5:8
  ) %>% 
  tab_spanner(
    label = md("**BIC**"),
    columns = vars(BIC, delta_BIC_within, delta_BIC_across)
  ) %>% 
  tab_spanner(
    label = md("**AIC**"),
    columns = vars(AIC, delta_AIC_within, delta_AIC_across)
  ) %>% 
  cols_label(
    delta_BIC_within = html("&Delta; BIC<sub>within</sub>"),
    delta_BIC_across = html("&Delta; BIC<sub>across</sub>"),
    delta_AIC_within = html("&Delta; AIC<sub>within</sub>"),
    delta_AIC_across = html("&Delta; AIC<sub>across</sub>")
  ) -> gt_table_bic

gtsave(gt_table_bic, "aic_bic_table.png")  
```

```{r eval=FALSE}
knitr::include_graphics("aic_bic_table.png")
```

@@

#References
